Vragenlijst thesis evaluatie

### 2015-08-12 doc/template/chap-4.tex
laatste van gisteren

The overview of this chapter will be as follows: Section \ref{methodsofpropagation} presents an overview of the most frequently used propagation methods by worms. These propagation methods will be covered by different kinds of models in section \ref{modelsforpropagation} presents models to determine the time a worm needs to infect a sufficient number of nodes. These results can be used for the completion of parameter \textit{d}. \todo{wat wordt er met de vorige zin bedoeld?} Finally, section \ref{eigenmatrixmethode}, introduces an easy method to calculate the delay of the propagation of a worm. % Different kind of graphs to model a computer network are introduced.

>>>>

The overview of this chapter will be as follows: Section \ref{methodsofpropagation} presents an overview of the most frequently used propagation methods by worms. These propagation methods will be covered by different kinds of models in section \ref{modelsforpropagation} illustrates a couple of models as examples to determine the propagation of a worm. These models can be used to extract parameter \textit{d}. Section \ref{eigenmatrixmethode} introduces an easy method to calculate the delay of the propagation of a worm. In the last section \ref{GoogleMatrix}, a method based on the PageRank algorithm of Google is used to determine which node has a higher probability of being infected by a worm. % Different kind of graphs to model a computer network are introduced.
